\begin{thebibliography}{00}
\bibitem{b1}1. GBD 2019 Blindness and Vision Impairment Collaborators; Vision Loss Expert Group of the Global Burden of Disease Study. Causes of blindness and vision impairment in 2020 and trends over 30 years, and prevalence of avoidable blindness in relation to VISION 2020: the Right to Sight: an analysis for the Global Burden of Disease Study. Lancet Glob Health. 2021 Feb;9(2):e144-e160. doi: 10.1016/S2214-109X(20)30489-7.
\bibitem{b2}2. Visser C, Flohr Y, Trichter D. The state of web accessibility in 2024 (research report). AccessibilityChecker.org. 2024 Aug 2. Available from: https://www.accessibilitychecker.org/research-papers/the-state-of-web-accessibility-in-2024-research-report/
\bibitem{b3}3. Statcounter Global Stats. Browser market share worldwide. Statcounter. 2025 Apr 19. Available from: https://gs.statcounter.com/browser-market-share.
\bibitem{b4}4. Hamideh Kerdar, S., Bächler, L. \& Kirchhoff, B.M. The accessibility of digital technologies for people with visual impairment and blindness: a scoping review. Discov Computing 27, 24 (2024). https://doi.org/10.1007/s10791-024-09460-7.
\bibitem{b5}5. Web Content Accessibility Guidelines (WCAG) 2.1. How to Meet WCAG (Quick Reference): W3C World Wide Web Consortium Recommendation; 2023. https://www.w3.org/WAI/WCAG22/quickref/?versions=2.1. Accessed 20 Apr 2025.
\bibitem{b6}6. Sajka J, Korn P, Hall C, Cooper M. Challenges with accessibility guidelines conformance and testing, and approaches for mitigating them. W3C Editor's Draft. 2025 Apr 1. Available from: https://w3c.github.io/wcag/conformance-challenges/
\bibitem{b7}7. Yash Prakash, Akshay Kolgar Nayak, Mohan Sunkara, Sampath Jayarathna, Hae-Na Lee, and Vikas Ashok. 2024. All in One Place: Ensuring Usable Access to Online Shopping Items for Blind Users. Proc. ACM Hum.-Comput.Interact. 8, EICS, Article 257 (June 2024), 25 pages. https://doi.org/10.1145/3664639
\bibitem{b8}8. Kodandaram SR, Uckun U, Bi X, Ramakrishnan IV, Ashok V. Enabling uniform computer interaction experience for blind users through large language models. In: Proceedings of the 26th International ACM SIGACCESS Conference on Computers and Accessibility (ASSETS '24). 2024. Article No.: 73, p. 1–14. Available from: https://doi.org/10.1145/3663548.3675605
\bibitem{b9}9. Mehendale S, Walishetti A. DexAssist: A voice-enabled dual-LLM framework for accessible web navigation. Illinois Mathematics and Science Academy, Aurora IL, USA. 2024. Available from: https://arxiv.org/pdf/2411.12214
\end{thebibliography}